### 2011-12-16 docs/src/manual.tex

\begin{titlepage}
\pdfbookmark[1]{Title}{Title}
\begin{center}
\fbox{
\begin{minipage}[t]{\figurewidth}
\begin{center}\vspace{10ex}
{\Huge\bf KiCS2 0.1}\\[4ex]
{\huge The Kiel Curry System (Version 2)}\\[7ex]
{\huge User Manual}\\[4ex]
Version of December 13, 2011\\[6ex]
\Large
Michael Hanus$^1$ [editor] \\[3ex]
{\large Additional Contributors:}\\[2ex]
Bernd Bra\ss{}el$^2$ \\
Bj\"orn Peem\"oller$^3$\\
Fabian Reck$^4$ \\[4ex]
\normalsize
(1) University of Kiel, Germany, {\tt mh@informatik.uni-kiel.de} \\
(2) University of Kiel, Germany, {\tt bbr@informatik.uni-kiel.de} \\
(3) University of Kiel, Germany, {\tt bjp@informatik.uni-kiel.de} \\
(4) University of Kiel, Germany, {\tt fre@informatik.uni-kiel.de} \\[5ex]~
\end{center}
\end{minipage}}
\end{center}
\end{titlepage}

@@

\item[\fbox{\code{choices}}]\pindex{choices}
Show the internal choice structure
(according to the implementation described in
\cite{BrasselHanusPeemoellerReck11})
resulting from the complete evaluation of the main expression.
This mode is only useful for debugging purposes.

\item[\fbox{\code{supply $i$}}]\pindex{supply}
Use the implementation $i$ for the identifier supply for choice structures
(see \cite{BrasselHanusPeemoellerReck11} for a detailed explanation).
Currently, the values \code{ghc} (default), \code{integer},
or \code{ioref} are supported for $i$.

>>>>

\begin{titlepage}
\pdfbookmark[1]{Title}{Title}
\begin{center}
\fbox{
\begin{minipage}[t]{\figurewidth}
\begin{center}\vspace{10ex}
{\Huge\bf KiCS2 0.1}\\[4ex]
{\huge The Kiel Curry System (Version 2)}\\[7ex]
{\huge User Manual}\\[4ex]
Version of December 16, 2011\\[6ex]
\Large
Michael Hanus$^1$ [editor] \\[3ex]
{\large Additional Contributors:}\\[2ex]
Bernd Bra\ss{}el$^2$ \\
Bj\"orn Peem\"oller$^3$\\
Fabian Reck$^4$ \\[4ex]
\normalsize
(1) University of Kiel, Germany, {\tt mh@informatik.uni-kiel.de} \\
(2) University of Kiel, Germany, {\tt bbr@informatik.uni-kiel.de} \\
(3) University of Kiel, Germany, {\tt bjp@informatik.uni-kiel.de} \\
(4) University of Kiel, Germany, {\tt fre@informatik.uni-kiel.de} \\[5ex]~
\end{center}
\end{minipage}}
\end{center}
\end{titlepage}

@@

\item[\fbox{\code{choices}}]\pindex{choices}
Show the internal choice structure
(according to the implementation described in
\cite{BrasselHanusPeemoellerReck11})
resulting from the complete evaluation of the main expression
in a tree-like structure.
This mode is only useful for debugging or
understanding the implementation of non-deterministic
evaluations used in KiCS2.

\item[\fbox{\code{supply $i$}}]\pindex{supply}
Use implementation $i$ as the identifier supply for choice structures
(see \cite{BrasselHanusPeemoellerReck11} for a detailed explanation).
Currently, the following values for $i$ are supported:
\begin{description}
\item[\code{integer}:]\pindex{integer}
Use unbounded integers as choice identifiers.
This implementation is described in \cite{BrasselHanusPeemoellerReck11}.
\item[\code{ghc} (default):]\pindex{ghc}
Use a more sophisticated implementation of choice
identifiers (based on the ideas described in \cite{AugustssonRittriSynek94})
provided by the Glasgow Haskell Compiler.
\item[\code{pureio}:]\pindex{pureio}
Use IO references (i.e., memory cells) for choice identifiers.
This is the most efficient implementation for top-level depth-first search
but cannot be used for more sophisticated search methods
like encapsulated search.
\item[\code{ioref}:]\pindex{ioref}
Use a mixture of \code{ghc} and \code{pureio}.
IO references are used for top-level depth-first search
and \code{ghc} identifiers are used for encapsulated search methods.
\end{description}
